---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SKconvienience

<!-- badges: start -->
[![R-CMD-check](https://github.com/follhim/SKconvienience/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/follhim/SKconvienience/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

SKconvienience is a package with convenience functions for all things R stats.

## Installation

You can install the development version of SKconvienience from [GitHub](https://github.com/follhim/SKconvienience) with:
``` r
# Install devtools if you don't have it
install.packages("devtools")

# Install SKconvienience
devtools::install_github("follhim/SKconvienience")
```

## Example

### Basic correlation table
```{r example, eval=FALSE}
library(SKconvienience)

# Create an APA-style correlation table
apa_cor_table(mtcars[, 1:5])
```

### With shifted descriptives

Display descriptive statistics as rows at the bottom instead of columns:
```{r shifted, eval=FALSE}
apa_cor_table(mtcars[, 1:5], shift.descriptives = TRUE)
```

### Export to Excel
```{r excel, eval=FALSE}
apa_cor_table(mtcars[, 1:5], filename = "my_correlation_table.xlsx")
```

## Citation

To cite this package in publications:
```{r citation, eval=FALSE}
citation("SKconvienience")
```

Or use:

> Kim, S. (2025). SKconvienience: A package for convenience in statistics (Version 0.0.0.9). https://follhim.github.io/SKconvienience/
